\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-23 paper/experiments.tex
Add results for acs_dirty query

% TODO MJS
In many cases, applying the imputation step at the base table simply is not an option. To
illustrate the increasing difficulty of such an approach as datasets scale, we used a simple
aggregate query over the ACS dataset in our final experiment(Figure~\ref{query-acs}).
Applying the imputation operation to the base table is extremely expensive, in our case the
process did not terminate within 20 minutes. In contrast, \ProjectName{} executes a
quality-optimized version in 9 seconds and a runtime-optimized version in 1 second. This
highlights the potential benefit of using our system for early data exploration.

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is prohibitive.
    \ProjectName's quality-optimized and performance-optimized
    query execute in 9 seconds and 1 second, respectively.
}%TODO MJS
\label{query-acs}
\end{figure}

>>>>

In many real-world cases, applying the imputation step at the base table is prohibitive.
To illustrate the increasing difficulty of such an approach as datasets scale, we used a simple
aggregate query over the ACS dataset in our final experiment(Figure~\ref{query-acs}).
Applying the imputation operation to the base table is extremely expensive, in our case
completing in 75 minutes. In contrast, \ProjectName{} executes a quality-optimized version
in 7 seconds and a runtime-optimized version in 1 second. This highlights the potential
benefit of using our system for early data exploration.

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is prohibitive.
    \ProjectName's quality-optimized and performance-optimized queries execute in 7 seconds
    and 1 second, respectively.
}
\label{query-acs}
\end{figure}
